FinalManuscript_DISCS_UG

### 2018-10-07 parts/02_relatedliterature_01cryptoimg.tex
Final final changes

\section{CryptoImg}
A paper published in 2009 by Ziad, et. al. attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure*}
The CryptoImg library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by CryptoImg allow all image processing operations to be performed on the server. However, due to limitations in the Pallier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

@@

We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research. First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented. We propose additional protocols to support more computationally intensive intensity transformations.
Second, the \textit{CryptoImg} library only considered the Pallier cryptosystem. We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.

>>>>

\section{CryptoImg}
A paper published in 2009 by Ziad, et. al. attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure*}
The \textit{CryptoImg} library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server. However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

@@

We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research. First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented. We propose additional protocols to support more computationally intensive intensity transformations.
Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem. We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Final final changes

\subsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damgård, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.

>>>>

\subsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.

### 2018-10-07 parts/02_relatedliterature_06fullyhomomorphic.tex
Final final changes

We will present two such cryptosystems, the Dasgupta-Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

\subsection{The Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.

@@

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta-Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta-Pal cryptosystem are accomplished using few arithmetic operations.

\subsection{HElib and the BGV Cryptosystem}
The BGV (Brakerski-Gentry-Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem. The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.

@@

The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license. The Pyfel library is a Python API for the HElib library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
\begin{itemize}
	\item Arithmetic operations: addition, subtraction, multiplication;
	\item Binary operations: AND, OR, NOT, XOR.
\end{itemize}

>>>>

We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

\subsection{The Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.

@@

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.

\subsection{HElib and the BGV Cryptosystem}
The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem. The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.

@@

The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license. The Pyfhel library is a Python API for the HElib library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
\begin{itemize}
	\item Arithmetic operations: addition, subtraction, multiplication;
	\item Binary operations: AND, OR, NOT, XOR.
\end{itemize}

### 2018-10-07 parts/03_methodology.tex
Final final changes

Four homomorphic encryption schemes will be investigated. For cryptosystems with readily available open-source implementations, such implmentations will be used. For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta-Pal cryptosystem will be implemented from scratch.
\end{itemize}

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up?
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.

@@

Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
\section{Summary}
In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

>>>>

Four homomorphic encryption schemes will be investigated. For cryptosystems with readily available open-source implementations, such implmentations will be used. For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem will be implemented from scratch.
\end{itemize}

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up?
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training data will be secured from the \texttt{faces94} database (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

@@

Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.

\section{Summary}
In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}
